---
title: "Select Hail Events - GVZ Loss Data"
author: "Mirco Heidemann"
date: "19 5 2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(sf)

path_data <- here("Model/data/")
path_tbl <- here("Model/tables")

```

*Select Hailevents*
Select hail events from GemDat/Rubin Database, relevant from a GVZ perspective. Let's define a hail loss event if there are at least 800 claims reported.
Index the loss data:
loss_index = index_2021 / index_jahr_i * schad_geschaetzt_jahr_i

```{r import}
file_name <- here(path_data, "GVZ_Hail_Loss_200001_to_202203.csv")

df_data <- read_delim(file_name, delim = ';',
                      show_col_types = FALSE) %>% 
  mutate(schad_index = round(max(Index) / Index * Schadensumme))
```

Generate table per relevant hail events, sort in descending order according the number of reported claims
```{r tabel}
tbl_events <- df_data %>% 
  dplyr::select(Schadendatum, schad_index) %>% 
  mutate(Schadendatum = as.Date(Schadendatum, "%d%m%Y")) %>% 
  group_by(Schadendatum) %>% 
  summarise(loss_index = round(sum(schad_index)),
            reported_claims = n()) %>% 
  #filter(reported_claims > 999) %>% 
  filter(reported_claims > 799) %>% 
  arrange(desc(Schadendatum))

# tbl_events
```
Now we have our hail events!

Remarks:
- 01. & 02.08.2017 counts as two events
- 12. & 13.07.2021 counts as one event: Put claims from 12.07. to the 13.07.2021 event
- We only have radar date from 2004 on

Generate one CSV Table per each event (put claims from 12.07. to the 13.07.2021 event) but first, do some data wranling:
- Exclude zero losses
- Transform Coordinate from LV95 to LV03 (MeteoSwiss codes radar images in old LV03!)

```{r}
## Coord transform with the sf-package:
## ---

## First define coord.system, ...
df_point <- df_data %>%
  st_as_sf(coords = c("KoordinateOst", "KoordinateNord"), crs = 2056)
## ... then transform into the LV03 coordinat system
df_lv03 <- st_transform(df_point, 21781)

## Write point geometry coords in separate columns
df_lv03 <- df_lv03 %>%
  mutate(geox = unlist(map(df_lv03$geometry,1)),
         geoy = unlist(map(df_lv03$geometry,2)))

## Convert geo feature tibble into data frame
df_lv03 <- data.frame(df_lv03) %>% 
  dplyr::select(-geometry) %>% 
  filter(schad_index > 0) %>% 
  mutate(Schadendatum = as.Date(Schadendatum, "%d%m%Y"))

# summary(df_lv03)
## ---
```

Generate one CSV Table per each event (put claims from 12.07. to the 13.07.2021 event).
```{r}
## TO DO FOR LOOP
tbl_event_selected <- tbl_events %>% 
  filter(Schadendatum > as.Date("01012004", "%d%m%Y"))

df_event <- df_lv03 %>% 
  filter(Schadendatum == tbl_event_selected$Schadendatum[1])

out_file <- paste0("Eventloss_", format(tbl_event_selected$Schadendatum[1], "%Y%m%d"), ".csv")
  
write_excel_csv(df_event, here(path_tbl, out_file), delim = ";")

cat("\n\n")
cat("csv-file saved:", here(path_tbl, out_file))
```